Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
intermediate commit

\begin{itemize}
        \item[(R1)] \textbf{Lexical choice}: is mostly met by both data sets, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
		\item[(3)] \textbf{Contextual informativeness}: is not met, as not all objects were annotated with REs and corresponding categories
\end{itemize}

@@

>>>>

\begin{itemize}
        \item[(1)] \textbf{Lexical choice}: is mostly met by both data sets, though it is unclear how the additional constraints in RefCoco+ impact on the naturalness of object naming
		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
		\item[(3)] \textbf{Contextual informativeness}: is not met, as not all objects were annotated with REs and corresponding categories
\end{itemize}

@@

\paragraph{Shortcomings}

By design, \flickr can be used to study the way people refer to individual entities in an image depending on the situation the speakers describe and,  
in contrast to \refcoco(+), the production of entity mentions did not underlie any constraints. 
On the other hand, \flickr is less suited for referring expression generation since mentions in isolation of their linguistic context may not uniquely identify the referred object.

\begin{itemize}
        \item[(1)] \textbf{Lexical choice}: is met, though object names might not be fully discriminative (as in referring expressions)
		\item[(2)] \textbf{Lexical candidates}: is not met, as we only have access to basic-level categories and cannot retrieve the  most specific category or name for each object
		\item[(3)] \textbf{Contextual informativeness}: is not met, as not all objects were annotated with REs and corresponding categories
\end{itemize}

\subsection{Flickr30k Entities}~\\
The \flickr dataset \cite{plummer2015flickr30kentities}\footnote{Available at  \url{web.engr.illinois.edu/~bplumme2/Flickr30kEntities}}  augments Flickr30k, a dataset of 30k~images and five sentence-level captions for each of the images, with region-level annotations. 
Specifically, mentions of the same entities across the five captions of an image are linked to the bounding boxes of the objects they refer to. 
The dataset was designed to advance image description generation and phrase localization in particular (e.g.,~\cite{rohrbach2016grounding,plummer2017phrase,yeh2018unsupervised}).
